Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-07 WRITEUP/ms.tex
abstract

\begin{abstract}
We study the dynamical properties of molecular clouds and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
kinetic and thermal energies. 
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with large velocity dispersion ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe as well as at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order $10^{6.5-8}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
corresponds to the arms of the main disk of \flower and breaks down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
We find that the ...
The MCs in the satellites..
consistent with PVE.
We find no temporal variations in the MC physical properties over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. Higher resolution cosmological zoom-in simulations 
will shed light into ... , as we .... from observations.
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
kinetic and thermal energies. 
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) that are comparable to 
those observed in gas-rich galaxies in the local universe as well as at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order $10^{6.5-8}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the main disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
which sets the scales for fragmentation.
We compare the dynamics of MCs in \flower and those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are systematically found to have higher $\sigma$ and $\Sigma$ regardless of the $n_{\rm cut}$ adopted.
The higher velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the molecular substructures, likely 
because \flower has experienced more episodes of recent \SF, and thus stronger SNe and stellar feedback.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
On the other hand, we find $\alpha_{\rm vir}$\ssim1 for MCs in the satellite galaxies. We interpret this as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, where at the EoR, \SF continues as gas is being accretion from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
Higher resolution cosmological zoom-in simulations will ... shed light into ... , as we .... from observations with ALMA.
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}
